Bird beak's elaboration and innovation

### 2022-08-04 Analysis/04-Figure3_with_ellipse_scalling_and_8D_histograms.Rmd
Update 04-Figure3_with_ellipse_scalling_and_8D_histograms.Rmd

box_size <- 1.5
pdf(file = "../Manuscript/Figures/Figure3_ellipses.pdf", height = box_size*10, width = box_size*10)

@@

box_size <- 1.5
pdf(file = "../Manuscript/Figures/Figure3_passeriformes.pdf", height = box_size*9, width = box_size*10)

>>>>

box_size <- 1.5
pdf(file = "../Manuscript/Figures/ellipses.pdf", height = box_size*10, width = box_size*10)

@@

box_size <- 1.5
pdf(file = "../Manuscript/Figures/ellipses_passeriformes.pdf", height = box_size*9, width = box_size*10)
